Evaluation of probabilistic photometric redshift estimation approaches for \textsc{LSST}

### 2019-03-15 paper/tex/results.tex
spacing

Fig.~\ref{fig:pitqq} shows both the quantile-quantile plots (red) and the histogram of PIT values (blue) summarizing the results from each photo-$z$ code.  The red line shows the measured quantiles, while the black diagonal represents the ideal QQ values if the distribution were perfectly reproduced.  A second panel below the main panel for each code shows the difference between $Q_{\rm data}$ and $Q_{\rm theory}$, i.~e.~the departure from the diagonal, for clarity.
Biases and trends in whether the average width of the $p(z)$ values being over/under-predicted are evident.  An overall bias where the predicted redshift is systematically low manifests as the measured QQ value falling above the diagonal, as is the case for \textsc{BPZ} and \textsc{EAZY}, while a systematic overprediction shows up as the measured QQ value falling below the diagonal, as seen in \textsc{TPZ}.  In terms of PIT histograms, a systematic underprediction of redshift corresponds to fewer PIT values at $PIT<0.5$ and more at $PIT>0.5$, while a systematic overprediction will show the opposite.

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\centering
\caption{The fraction of ``catastrophic outlier'' PIT values.  We expect a value of 0.0002 for a proper Uniform distribution.  An excess over this small value indicates true redshifts that fall outside the non-zero support of the $p(z)$.  }\label{tab:pitoutlier}
\begin{tabular}{lc}
\hline
\hline
 ``catastrophic outlier''\\ PIT fraction\\
\hline
Photo-z Code & fraction PIT$<10^{-4}$ or $>$0.9999\\
\hline
\textsc{ANNz2} & 0.0265\\
\textsc{BPZ} & 0.0192\\
\textsc{Delight} & 0.0006\\
\textsc{EAZY} & 0.0154\\
\textsc{FlexZBoost} & 0.0202\\
\textsc{GPz} & 0.0058\\
\textsc{LePhare} & 0.0486\\
\textsc{METAPhoR}& 0.0229\\
\textsc{CMNN} & 0.0034\\
\textsc{Skynet} & 0.0001\\
\textsc{TPZ} & 0.0130\\
\hline
\textsc{TrainZ} & 0.0002\\
\end{tabular}
\end{table}

>>>>

Fig.~\ref{fig:pitqq} shows both the QQ plots and the histogram of PIT values, QQ plot, and a QQ difference plot relative to the ideal diagonal.
Biases and trends in whether the average width of the $p(z)$ values being over/under-predicted are evident.
An overall bias where the predicted redshift is systematically low manifests as the measured QQ value falling above the diagonal, as is the case for \textsc{BPZ} and \textsc{EAZY}, while a systematic overprediction shows up as the measured QQ value falling below the diagonal, as seen in \textsc{TPZ}.
In terms of PIT histograms, a systematic underprediction of redshift corresponds to fewer PIT values at $PIT<0.5$ and more at $PIT>0.5$, while a systematic overprediction will show the opposite.

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\centering
\caption{The fraction of ``catastrophic outlier'' PIT values.
We expect a value of 0.0002 for a proper Uniform distribution.
An excess over this small value indicates true redshifts that fall outside the non-zero support of the $p(z)$.}
\label{tab:pitoutlier}
\begin{tabular}{lc}
\hline
\hline
 ``catastrophic outlier''\\ PIT fraction\\
\hline
Photo-z Code & fraction PIT$<10^{-4}$ or $>$0.9999\\
\hline
\textsc{ANNz2} & 0.0265\\
\textsc{BPZ} & 0.0192\\
\textsc{Delight} & 0.0006\\
\textsc{EAZY} & 0.0154\\
\textsc{FlexZBoost} & 0.0202\\
\textsc{GPz} & 0.0058\\
\textsc{LePhare} & 0.0486\\
\textsc{METAPhoR}& 0.0229\\
\textsc{CMNN} & 0.0034\\
\textsc{Skynet} & 0.0001\\
\textsc{TPZ} & 0.0130\\
\hline
\textsc{TrainZ} & 0.0002\\
\end{tabular}
\end{table}
